---
title: "COVID Trends"
author: "Mohamed Abed"
date: "7/29/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Intro

- COVID Trends is an application to present data about New Corona Virus Panademic.
- Data obtained from this [kaggle link.](https://www.kaggle.com/sudalairajkumar/novel-corona-virus-2019-dataset?select=covid_19_data.csv)  

- You can choose desired country from list of countries and choose type of cases of analysis (ex. confirmed). Then, a plot will be drawn to represent data. Also a summation of the number of cases will appear below.

- COVID Trends Application can be accessed though this [link.]()

## Code - Example 1

```{r echo=TRUE, eval= FALSE}
# obtain data
data=read.csv("covid_19_data_month.csv")
# choose country and type of cases
country="Egypt"
target="confirmed"
data= data[data$country==country,]
# plot
x <- data[, "Month"]
y <- data[,target]
plot(x,y,type='l',col=1,lwd=4,xlab='Month',ylab="No. of Confirmed Cases")
#summary
paste('Total',target,'Cases in',country,': ',max(data[,target]))

```

## Plot - Example 1

```{r echo=FALSE, message=FALSE, warning=FALSE}
# obtain data
data=read.csv("covid_19_data_month.csv")
# choose country and type of cases
country="Egypt"
target="confirmed"
data= data[data$country==country,]
# plot
x <- data[, "Month"]
y <- data[,target]
plot(x,y,type='l',col=1,lwd=4,xlab='Month',ylab="No. of Confirmed Cases")
#summary
paste('Total',target,'Cases in',country,': ',max(data[,target]))
```

## Code - Example 2

```{r echo=TRUE, eval= FALSE}
# obtain data
data=read.csv("covid_19_data_month.csv")
# choose country and type of cases
country="US"
target="recovered"
data= data[data$country==country,]
# plot
x <- data[, "Month"]
y <- data[,target]
plot(x,y,type='l',col=3,lwd=4,xlab='Month',ylab="No. of Recovered Cases")
#summary
paste('Total',target,'Cases in',country,': ',max(data[,target]))

```

## Plot - Example 2

```{r echo=FALSE, message=FALSE, warning=FALSE}

# obtain data
data=read.csv("covid_19_data_month.csv")
# choose country and type of cases
country="US"
target="recovered"
data= data[data$country==country,]
# plot
x <- data[, "Month"]
y <- data[,target]
plot(x,y,type='l',col=3,lwd=4,xlab='Month',ylab="No. of Recovered Cases")
#summary
paste('Total',target,'Cases in',country,': ',max(data[,target]))
```
